The Prevalence of E-Mail Header Injections on the World Wide Web

### 2016-05-24 rel_work.tex
fixed related work, starting ethics

% Adam: Sai, can you combine all the \cites at the same line like I did for the others? 
There are different approaches to finding vulnerabilities in web applications, and most approaches will be either Black-Box testing or White-Box testing.
Our work is based on the black-box testing approach to finding vulnerabilities on websites, and research has made use of this methodology to find vulnerabilities in web applications~\cite{Beizer:1995:BTT:202699}, \cite{Huang}, \cite{kals2006secubat}, \cite{payet13:ears-in-the-wild}, \cite{zanero2005automatic}. There has been significant discussion on both the benefits of such an approach~\cite{black-box} and its shortcomings~\cite{Doupe2012}, \cite{Doupe2010}.

Our work does not intend to act as a vulnerability scanner, but as a means to identify an \ehi vulnerability in a given web application. In this sense, because we are injecting payloads into the web application, our work is related to other injection based attacks, such as SQL Injection~\cite{sql1}, \cite{sql0}, \cite{sql2}, Cross-Site Scripting \cite{Injection1}, \cite{KleinAmit}, HTTP Header Injection~\cite{sessionride}, and the related Simple Mail Transfer Protocol (SMTP) Injection~\cite{Terada2015}.

@@

The first documented article dates to over a decade ago; a late 2004 article on phpsecure.info~\cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how this vulnerability existed in the reference implementation of the mail function in PHP, and how it can be exploited. Following this, we found other blog posts~\cite{Calin}, \cite{DK}, \cite{Injection2}, \cite{Nicol}, \cite{Pope}, each describing how to exploit the vulnerability by using newlines to camouflage headers inside user input. A wiki entry~\cite{Injection} also describes the ways to prevent such an attack. However, none of these articles have performed these attacks against real-life websites.

>>>>

% Adam: Sai, can you combine all the \cites at the same line like I did for the others? 
There are different approaches to finding vulnerabilities in web applications, and most approaches will be either Black-Box testing or White-Box testing.
Our work is based on the black-box testing approach to finding vulnerabilities on websites, and research has made use of this methodology to find vulnerabilities in web applications~\cite{Beizer:1995:BTT:202699, Huang, kals2006secubat, payet13:ears-in-the-wild, zanero2005automatic}. There has been significant discussion on both the benefits of such an approach~\cite{black-box} and its shortcomings~\cite{Doupe2012, Doupe2010}.

Our work does not intend to act as a vulnerability scanner, but as a means to identify an \ehi vulnerability in a given web application. In this sense, because we are injecting payloads into the web application, our work is related to other injection based attacks, such as SQL Injection~\cite{sql1, sql0, sql2}, Cross-Site Scripting \cite{Injection1, KleinAmit}, HTTP Header Injection~\cite{sessionride}, and the related Simple Mail Transfer Protocol (SMTP) Injection~\cite{Terada2015}.

@@

The first documented article dates to over a decade ago; a late 2004 article on phpsecure.info~\cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how this vulnerability existed in the reference implementation of the mail function in PHP, and how it can be exploited. Following this, we found other blog posts~\cite{Calin, DK, Injection2, Nicol, Pope}, each describing how to exploit the vulnerability by using newlines to camouflage headers inside user input. A wiki entry~\cite{Injection} also describes the ways to prevent such an attack. However, none of these articles have performed these attacks against real-life websites.
